---
title: "assignment_b1"
author: "Harrison"
date: "2022-10-31"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assignment B-1

This assignment covers making a function in R, documenting it, and testing it.

```{r}
library(tidyverse)
library(testthat)
library(gapminder)
library(palmerpenguins)
```

# Creating Function

```{r}
#' @title group_mean function
#' 
#' @details Groups specified observations together and provides the mean of a chosen numeric variable
#' 
#' @param df dataframe being used for analysis
#' 
#' @param group, observational group which you would like to organize data by
#' 
#' @param x, numeric variable which the mean will be taken from
#' 
#' @return returns the mean of a numeric variable for each group of observations
#' 

group_mean <- function(df, group, x, ..., na.rm = TRUE) {
  stopifnot(is.numeric(df %>%
                         pull({{x}})))
  
  df %>%
    group_by({{group}}) %>%
    summarise(mean = mean({{x}}, na.rm = na.rm))
  
}
```


# Examples of Function Use

Initial tests on the group_mean function using the gapminder dataset. We can expect that the output should have 2 columns, one containing the names of the observations that are grouped together, and a "mean" column containing the mean of the specified numeric variable for each obvservational group.

```{r}
# viewing dataset
head(gapminder)

# using group_mean to find the mean lifeExp for each country
group_mean(gapminder, country, lifeExp)

# using group_mean to find the mean gdpPercap of each continent
group_mean(gapminder, continent, gdpPercap)

# using group_mean to find the mean body_mass_g of penguin species where body_mass_g contains NA values
group_mean(penguins, species, body_mass_g)
```

We can see that so far group_mean is behaving as we expect it to. Now, let's see how the function performs when given some more formal stress tests.

# Testing

We can use the test_that function to perform more formal stress tests on the group_mean function.

```{r}
# testing that the function can take a vector that contains NA's, will produce a warning when given a string as an input, throw an error when trying to take the mean of a non-numeric vector, and throw an error when trying to take the mean of a vector of length 0.

# making a tibble to compare with group_mean output 
island_flip_length <- penguins %>%
  group_by(island) %>%
  summarise(mean = mean(flipper_length_mm, na.rm = TRUE))

# test_that function 

test_that("Testing group_mean function", {
  expect_equal(island_flip_length, group_mean(penguins, island, flipper_length_mm, na.rm = TRUE))
  expect_warning(group_mean(penguins, island, "flipper_length_mm"))
  expect_error(group_mean(penguins, species, sex))
  expect_error(group_mean(penguins, specied, numeric(0)))
})
```



