---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# groupmean

<!-- badges: start -->
<!-- badges: end -->

The goal of groupmean is to quickly find the means of categorical variables of interest. By specifying dataframe, a categorical variable, and a numeric variable to the function, the categorical variable will be grouped by each unique observation and the mean of a numeric variable in question will be returned for each group.

## Installation

You can install the development version of groupmean like so:

``` r
devtools::install_github("stat545ubc-2022/assignment_b1_b2_harrison_mar/groupmean")
```

## Example

This is a basic example which shows you how to solve a common problem using the gapminder dataset:

```{r example}
library(groupmean)
library(gapminder)

# using group_mean to find the mean lifeExp for each country
group_mean(gapminder, country, lifeExp)

# using group_mean to find the mean gdpPercap of each continent
group_mean(gapminder, continent, gdpPercap)

```
